material and methods

### 2017-05-31 man/ms_material_methods.Rmd
update ms_mm
update methods

@@

```{r}
py <- pointer.rgc(s033, nb.yrs=4, rgc.thresh.pos=60, rgc.thresh.neg=40, series.thresh=75)

rgc.plot(py,start.yr=1950,end.yr=NULL,sd.disp=FALSE
```

>>>>

## Tree sampling 
Samplig was carried during autumn of 2016. Trees were sampled at two locations located in contrasting slopes of Sierra Nevada: San Juan (SJ; northern site) and Cáñar (CA; southern site) (Table 1). Both sites were oak monospecific and representatives of two of the three the population's cluster identified for this specie in this mountain range (:red_circle: mejorar; citar Pérz-Luque et al..). In each site between 15 and 20 dominant trees were sampled. Two cores of 5 mm of diameter were taken per tree at 1.3 m using an increment borer. Diameter at breat height (DBH) and total height were recorded for each tree. Increment cores were air dried, glued onto wooden mounts and sanded. Annual radial growth (ring width, RW) were measured with a LINTAB measuring device (:red_circle: Rinntech 2003) coupled to a stereomicroscope, with an accuracy of 0.01 mm. Individual ring series were visually and statistically cross-dated with TSAP software (:red_circle: Frank Rinn, Heidelberg, Germany), using the statistics Gleichläufigkeit (GLK), t-value and the crossdating index (CDI). Validation of the croos-dating was done using COFECHA software [@Holmes1983].

@@
